04_DESeq_sexes

### 2019-05-24 analysis/04_DESeq2_sexes.Rmd
new update to pca and total DEGs

allPC1s <- plot_grid(p1 + theme_noaxislabels, 
                     p1 + theme_noaxislabels, 
                     p1 + theme_noaxislabels,
                     p1 + theme_noaxislabels,
                     p1 + theme(legend.position = "none"),
                     p1 + theme(legend.position = "none"),
                     nrow = 3, rel_heights = c(0.3, 0.3, 0.4))

>>>>

allPC1s <- plot_grid(p1 + theme_noaxislabels, 
                     p1 + theme_noaxislabels, 
                     p1 + theme_noaxislabels,
                     p1 + theme_noaxislabels,
                     p1 + theme_noaxislabels,
                     p1 + theme_noaxislabels),
                     nrow = 3, rel_heights = c(0.3, 0.3, 0.4))
